### 2017-06-14 manuscript/manuscript.Rmd
Contributing to central repo

>>>>

### Contributing to a Central (GitHub) repository

Once another team member has set up Git on their own computer, and signed up for GitHub, they need to **clone** the remote GitHub repository onto their local computer. [TODO actually check that these steps are correct with a 'fresh' computer.]

To clone a repository, the new user must first navigate to an appropriate location on the computer where they would like to create the repository on their computer, for example their `username/Documents` folder. Once the appropriate location is found, cloning will create a new folder for the repo inside this folder.

```bash
git clone https://github.com/<username>/<reponame>.git
```

These new contributors can then work on their local copies as detailed in earlier parts of this tutorial; making changes, adding, and committing. After committing their changes, they can update the status of the Central Git repo by pushing their changes to it:

```bash
git push
```
